---
title: "Kimberly Jonas' GitHub"
---
# ◕ヮ◕)ﾉ*:･ﾟ✧Kimberly Jonas(✿◡‿◡)

## About Me
  I am a graduate student at Baruch with an interest in data analytics, business intelligence, and research and decision making. Through my coursework and projects, I am developing experience with R, statistical analysis,
data visualization, and GitHub.

  My career interests center on using data to identify patterns, solve business problems, and communicate efficient solutions to stakeholders. I am a Business Analyst, which allows me to combine my analytical background and technical skills with research that I've always wanted to do.


## Education
**Baruch College**  
M.S. Business Analytics

**University of Notre Dame**
B.A. Psychology & French and Francophone Studies

(❁´◡`❁)(❁´◡`❁)

## Technical Skills
R | SQL | Excel | Python | GitHub

## Career Interests
- Data and Research Analysis
- Business Analysis
- Data Visualization

## GitHub
[Visit my GitHub profile](https://github.com/kjonass9)

☆*: .｡. o(≧▽≦)o .｡.:*☆(ﾉ◕ヮ◕)ﾉ*:･ﾟ✧


```{r}
#| echo: false
#| message: false
#| warning: false

library (leaflet)

gt_longitude <- -58.1551
gt_latitude  <- +6.8013

leaflet() |>
  addTiles() |>
  setView(gt_longitude, gt_latitude, zoom=10) |>
  addPopups(gt_longitude, gt_latitude, 
            "I'm from <b>here</b>!")
```

```{r}
#| include: false
1+1
```
--------------
Last Updated: `r format(Sys.time(), "%A %m %d, %Y at %H:%M%p")`